 

### 2021-06-28 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

Within-canopy leaf traits vary along the canopy light gradient, *i.e.,* in sun and shade leaves [@casasSunShadeLeaves2011], at a leaf anatomical, structural and biochemical level [@sackHowStrongIntracanopy2006; @niinemetsWorldwideAnalysisWithincanopy2015; @chenLeafEconomicsSpectrum2020]. 
This variation shapes vertical $T_{leaf}$ patterns [@fauset_differences_2018; @michaletzEnergeticCarbonEconomic2016]. Table `r table_leaf_traits`, summarizes relevant traits for thermal sensitivity. Further, research to characterize trait relationships and responses through the vertical canopy is needed, because LES theory was developed using mainly sun exposed (upper canopy) leaves [@chenLeafEconomicsSpectrum2020; @keenanGlobalLeafTrait2016].

>>>>

Within-canopy, leaf traits vary along the canopy light gradient [*i.e.,* in sun and shade leaves, @casasSunShadeLeaves2011] at a leaf anatomical, structural and biochemical level [Table `r table_leaf_traits`, @sackHowStrongIntracanopy2006; @niinemetsWorldwideAnalysisWithincanopy2015; @chenLeafEconomicsSpectrum2020]. 
This variation shapes vertical $T_{leaf}$ patterns [@fauset_differences_2018; @michaletzEnergeticCarbonEconomic2016]. 
Further research to characterize trait relationships and responses through the vertical canopy is needed, because LES theory was developed using mainly sun exposed (upper canopy) leaves [@chenLeafEconomicsSpectrum2020; @keenanGlobalLeafTrait2016].
